Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-06 paper.qmd
Updated Figure 11

## Compute hexbin parameters
num_bins_x_gau1 <- 22
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 62
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

>>>>

## Compute hexbin parameters
num_bins_x_gau1 <- 17
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 52
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)
